\textbf{Flatiron Health} \hfill Durham, North Carolina \\
Research Scientist, Statistical Programming \hfill 2025--present
\begin{itemize}
    \itemsep0em
    \item Lead statistical programmer across 5--8 concurrent studies (25$+$ total since joining Flatiron), translating analytic specifications from statistical analysis plans and protocols into R code to generate analytic datasets, descriptive and inferential statistics, and data visualizations — often involving novel variables, complex statistical methods, and non-standard RWE implementation.
    \item Manage a team of three statistical programmers (two India-based, one US-based); serve as hiring manager for permanent US-based position. Oversee workflow allocation, code review, and serve as point of contact for areas of methodological or implementation uncertainty. Coordinate with external managers on programmer capacity when working with non-direct reports.
    \item Subject matter expert (SME) on the Flatiron Health Research Database (FHRD) for Bladder Panoramic and SEER data; secondary SME for Breast Panoramic and NSCLC Panoramic datasets. Consult cross-functionally on data model nuances and appropriate use of Flatiron data modalities, including EHR-derived RWD, clinico-genomics, ML-extracted, and claims data.
    \item Collaborate daily with internal clinicians, epidemiologists, biostatisticians, and medical directors across study teams; engage directly with external pharmaceutical and biotech clients on client-sponsored research, serving as a technical point of contact for study implementation and data questions.
    \item Engage early in study lifecycle — reviewing protocols, table shells, and timelines in advance of programming — to ensure implementation clarity and identify methodological or data challenges before they arise.
    \item Serve as validation programmer on double-coding projects to ensure high-quality output; manage reconciliation between two independent programmers.
    \item Lead initiative to incorporate statistical programming guidance into table shells via an AI agent, including personally collecting and contributing guidance documentation from across Research Sciences.
    \item Contribute to team coding library reflecting table shell standardization, reducing redundant logic development across the programming team and improving efficiency and consistency of study delivery.
    \item Implement AI-assisted workflows for table shell generation, code review, and output quality control, contributing to continuous improvement of Flatiron's analytical tooling and programming standards.
    \item Team received 1st place in the Flatiron@Scale category of the 2025 company-wide hackathon for \textit{Real-World Utilization of ctDNA and Its Impact on Bladder Cancer Management}.
    \item Apply solid working knowledge of oncology treatment paradigms, tumor biology, and cancer epidemiology across multiple tumor types to inform analytic decisions and contribute meaningfully to scientific discussions with clinical colleagues.
    \item Co-Lead, Parent Employee Resource Group (ERG); manage \$10,000 budget and lead planning for Take Your Kid to Work Day ($100+$ employees); participate in leadership development programming including training in change management and organizational leadership.
\end{itemize}

\bigskip
\textbf{Collaborative for Financial Equity and Inclusion, The Ohio State University} \hfill Columbus, Ohio \\
Post Doctoral Researcher \& Adjunct Lecturer \hfill 2024--2025
\begin{itemize}
    \itemsep0em
    \item Lead analyst on large interdisciplinary team of PhDs, MDs, and Biostatisticians across 10$+$ projects focused on health economics. One project featured in \href{https://www.usatoday.com/story/money/2024/04/26/spouse-dies-credit-score-effect/73424579007/}{\color{lightblue}USA Today} and named \href{https://www.thinkadvisor.com/2023/12/26/cfp-board-picks-7-best-retirement-research-papers-of-2023/}{\color{lightblue}Top Retirement Research Paper of 2023}.
    \item Utilize latest econometric and statistical techniques to analyze EHR from multiple hospital systems and Cancer Registry data, including difference-in-differences, regression discontinuity, instrumental variables, and synthetic controls.
    \item Led management of the team's 17 TB of data on the Ohio Supercomputer, including secure data transfer via SFTP to/from hospital systems and state agencies using STATA, R, SQL, and Linux.
    \item Taught a 4000-level Decision Making course as instructor of record to approximately 20 juniors and seniors.
\end{itemize}

\medskip
\textbf{John Glenn College of Public Affairs, The Ohio State University} \hfill Columbus, Ohio \\
Doctoral Student Researcher \hfill 2019--2024
\begin{itemize}
    \itemsep0em
    \item Lead research assistant to multiple faculty members across departments of Public Policy, Economics, and Sociology. 
    \item Trained and mentored approximately fifteen analysts in data management, efficient coding, and data visualization, including writing a technical assessment for employment in the lab.
    \item Individually obtained \href{https://www.nber.org/programs-projects/projects-and-centers/8560-impact-household-cancer-diagnosis-investment-higher-education-labor-supply-and-financial?page=1&perPage=50}{\color{lightblue}\$15,000 in grant funding} from the National Bureau of Economic Research, completed dissertation, published numerous academic articles, and presented at national conferences.
    \item Received University Fellowship in Year 1. Nominated by department for Presidential Fellowship in Year 5.
\end{itemize}

\bigskip
\textbf{Cardinal Health, Inc.} \hfill Dublin, Ohio \\
Advanced Analytics Rotational Program \hfill 2016--2018
\begin{itemize}
    \itemsep0em
    \item \textit{Sales Analytics:} Lead analyst on territory rebalancing project using volume, sales performance, and geospatial data — awarded Best Advanced Analytics Project in 2017 company-wide. Also provided nearest neighbor benchmarking for multiple Health Networks using CMS data.
    \item \textit{Strategic Pricing:} Data analyst for specialty drugs and biosimilars pricing at one of the three largest pharmaceutical distributors in the USA (\$200B+ annual revenue); implemented SAS automation for pricing decisions.
\end{itemize}