\subsection{Published}
\begin{itemize}
    \itemsep0.5em
    \item \textbf{Pesavento, M.T.} (2022). The impact of direct to consumer shipping laws on the number and size distribution of U.S. wineries. \textit{Journal of Wine Economics}, 1-26. doi:10.1017/jwe.2022.49
    \item Dormady, N., Roa-Henriquez, A., Hoyt, M., \textbf{Pesavento, M.}, Koenig, G., Welch, W., \& Li, Z (2025). How are retail prices formed in restructured electricity markets?. \textit{Energy Economics}, 143. doi:10.1016/j.eneco.2025.108243
    \item \textbf{Pesavento, M.}, Loibl, C., Moulton, S., et al. (2025). Type 2 diabetes and financial outcomes. \textit{JAMA Network Open}, 8(7), e2523453. doi:10.1001/jamanetworkopen.2025.23453
\end{itemize}

\subsection{Conference Abstracts}
\begin{itemize}
    \itemsep0.5em
    \item Patel, K., Zhao, D., Fidyk, E., Hankinson, E.A., Mehta, A.M., \textbf{Pesavento, M.}, and Sujenthiran, A. (2026). Prognostic value of post-operative circulating tumor DNA (ctDNA) in real-world treatment and outcomes among patients with muscle invasive and locally advanced bladder cancer. \textit{Journal of Clinical Oncology}, 44(16\_suppl), 4600. doi:10.1200/JCO.2026.44.16\_suppl.4600
\end{itemize}

\subsection{Reports \& White Papers}
\begin{itemize}
    \itemsep0.5em
    \item Ryals, C., Mbah, O., \textbf{Pesavento, M.}, Castellanos, E., Ho, G., and Madison, A. (2026). \href{https://mycoa.communityoncology.org/publications/studies-and-reports/quality-of-care}{COA Quality of Care Study: Phase 1 report on overall survival. Flatiron Health \& Community Oncology Alliance.}
\end{itemize}

\subsection{Working Papers}
\begin{itemize}
    \itemsep0.5em
    \item Divers, S.F., Gordan, L., Mbah, O.M., Castellanos, E., Ferreyros, N., Ho, G., \textbf{Pesavento, M.}, and Ryals, C.A. Quality of care in US community oncology practices among patients with metastatic breast cancer (mBC) and metastatic non-small cell lung cancer (mNSCLC).
    \item Bruno, D., Sheffield, K., Brnabic, A., Ma, Q., Singh, R., Thoele, K., Puri, T., Flores Avile, C., Schwed, K., Bye, M., Mehta, A.M., and \textbf{Pesavento, M.} Real-world outcomes with chemoradiation and durvalumab consolidation in stage III KRAS G12C--mutant NSCLC in the US.
    \item Moulton, S., Brown, M., Haurin, D., Loibl, C., and \textbf{Pesavento, M.} Economic security of older adults after the death of a partner: evidence from credit data. Featured in \href{https://www.usatoday.com/story/money/2024/04/26/spouse-dies-credit-score-effect/73424579007/}{\color{lightblue}USA Today}; named \href{https://www.thinkadvisor.com/2023/12/26/cfp-board-picks-7-best-retirement-research-papers-of-2023/}{\color{lightblue}Top Retirement Research Paper of 2023}.
    \item Loibl, C., Drost, M., Campbell, Z., Moulton, S., Haurin, D., \textbf{Pesavento, M.}, Hyer, M., Einstadter, D., Perzynski, A.T., and Joseph, J.J. Credit scores, credit risk profiles, and glycemic control among patients with type 2 diabetes.
    \item \textbf{Pesavento, M.} The effects of type II diabetes on financial distress and labor supply: evidence from administrative data.
    \item \textbf{Pesavento, M.} The effects of household cancer diagnosis on investment in higher education. \textit{Funded by NBER and Sloan Foundation.}
    \item \textbf{Pesavento, M.} The impact of household cancer diagnosis on the labor supply of young adults. \textit{Funded by NBER and Sloan Foundation.}
    \item Chanda, T., Collins, M., Moulton, S., \textbf{Pesavento, M.}, and Rhodes, A. Mind the gap: state reductions in unemployment insurance and credit use among vulnerable households.
    \item \textbf{Pesavento, M.}, Dormady, N., and Greenbaum, R. Moderating the effects of advising characteristics: evidence from a controlled experiment.
\end{itemize}

\subsection{In Preparation}
\begin{itemize}
    \itemsep0.5em
    \item \textbf{Pesavento, M.}, Maltz, R., and Moulton, S. The impact of chronic health shocks in children on household labor supply and financial distress.
    \item Moulton, S., Padamsee, T., Loibl, C., Brown, M., Haurin, D., and \textbf{Pesavento, M.} Credit disparities in widowhood by race and gender.
\end{itemize}